\section{Software and tools used}
\begin{itemize}
\item \LaTeX, used as typesetting system to build this document.
\item draw.io - \url{https://www.draw.io} - used to draw diagrams and mock-ups.
\item StarUML Free - \url{http://staruml.io/} - used to produce some of the diagrams contained in the document.
\item GitHub - \url{https://github.com} - used to manage the different versions of the document and to make the distributed work much easier.
\item GitHub Desktop, the GitHub official application that offers a seamless way to contribute to projects.
\end{itemize}
\section{Hours of work}
The absolute major part of the document was produced in group work. The approximate number of hours of work for each member of the group is the following:

\begin{itemize}
\item Giovanni Scotti: 40 hours
\item Marco Trabucchi: 35 hours
\end{itemize}

NOTE: indicated hours include the time spent in group work.

\section{Changelog}
Here are listed the changes and additions between different versions of the document:
\begin{itemize}
\item[V2] E-R diagram and UX diagram have been adjusted to be compliant with the "profile picture" specification;
\item[V2] Minor changes in "Profile Editor" mock-up, "GPS Car Unlock" sequence diagram and "End Ride" sequence diagram;
\item[V2] Added missing link from "ReservationManager" to "PaymentGateway" (fee payment) in Figure \ref{app_server_comps};
\item[V2] Added information about individual relations between session beans and the entity beans they use directly.
\end{itemize}
