\section{Software and tools used}
\begin{itemize}
\item \LaTeX, used as typesetting system to build this document.
\item draw.io - \url{https://www.draw.io} - used to draw diagrams and mock-ups.
\item GitHub - \url{https://github.com} - used to manage the different versions of the document and to make the distributed work much easier.
\item GitHub Desktop, the GitHub official application that offers a seamless way to contribute to projects.
\item Alloy Analyzer, used for analyzing our specifications.
\end{itemize}
\section{Hours of work}
The absolute major part of the document was produced in group work. The approximate number of hours of work for each member of the group is the following:

\begin{itemize}
\item Giovanni Scotti: \textasciitilde 65 hrs;
\item Marco Trabucchi: \textasciitilde 60 hrs;
\end{itemize}

NOTE: indicated hours include the time spent in group work.

\section{Changelog}
Here are listed the changes and additions between different versions of the document:
\begin{itemize}
\item[V2] Added assumptions 16 and 17;
\item[V2] Added functional requirement 7 in "Manage Payments";
\item[V2] Added missing arc "reservedCar" in the class diagram;
\item[V2] Fixed functional requirement 9 in "Use Car": "it being turned on" has been turned into "user authentication".
\item[V2] Modified functional requirement 1 in "End Ride": added "and ending the ride";
\item[V2] Added functional requirement 8 in "End Ride";
\item[V3] Added "profile picture" requirement in Section \ref{user_int};
\item[V3] Added Subsection 2.7 containing information and picture about the World and Machine interpretation of the system-to-be;
\end{itemize}
