\subsubsection{Purpose}
The system must prevent any user's unfair behavior. Whenever the user decides to reserve a car for a ride, he/she has a limited amount of time to reach the car and use it. This is reasonable because during this time nobody can rent that precise car. If the user does not come and use the reserved car, he/she must be penalized and fined by the system.

Moreover, in this case, the previously reserved car becomes available again and the system notify the bad user about the fine he/she has just received. Then the system talks to the payment handler which automatically charges the user.

\subsubsection{Scenario 1}
Negan is dancing at the disco with his friends when he realizes that it's very late. He opens the \emph{PowerEnJoy} application on his smartphone and checks for an available and nearby car to rent to go home. He finds one and reserve it.

Suddenly he notices a very beautiful girl and decides to speak to her in order to know her better. The clock is ticking and he forgets about his previous reservation. After more than one hour, Negan checks his mobile phone and notices the system has notified him about the expired reservation charging a fine.

\subsubsection{Use-case}
The pay fee use-case is shown in Table \ref{pay_fee_uc}.

\subsubsection{Functional requirements}
\begin{enumerate}
\item The system must not allow a car to be reserved for more than 1 hour;
\item The system must notify the user about the expired reservation;
\item The system automatically charges the user in case of reservation expiration;
\item If the reserved car is not picked-up by the user within 1 hour from the reservation, the system tags the car available again;
\end{enumerate}

\begin{table}[H]
\begin{center}
\begin{tabular}{p{0.3\textwidth} | p{0.7\textwidth}}
\hline
Actor & Bad user, payment handler\\
\hline
Goal & Goal 4\\
\hline
Input Condition & The user has reserved a car and he/she does not pick it up within 1 hour from the reservation\\
\hline
Event Flow & 
\begin{enumerate}
\item The system establish a connection to the payment handler;
\item The system asks the payment handler to charge the user a fee of 1 euro;
\end{enumerate} \\
\hline
Output Condition & The system notifies the user about the fine and tags the reserved car available again.\\
\hline
%Inserire errore nel pagamento?
Exception & None.\\
\hline
\end{tabular}
\end{center}
\caption{Pay fee use-case}
\label{pay_fee_uc}
\end{table}