\subsubsection{Purpose}
The user who wants to subscribe to the \emph{PowerEnJoy} service can carry out the registration process through the mobile application or the web one. First of all the user has to fill a registration form with his/her personal information and accept the Terms and Conditions agreement otherwise the procedure will be aborted.

As soon as the user submits the data, the system checks all the information and sends a confirmation email to the specified e-mail address including the password to access the service and the personal PIN required to start the car engine.

\subsubsection{Scenario 1}
Marta would like to register to the \emph{PowerEnJoy} rental service from her computer. She surfs the internet and opens the registration page by clicking on the "sign up" button located in the login page. She fills in the registration form and agrees the service Terms and Conditions. Then Marta submits everything to the system, that checks the personal data. Personal PIN and password are sent to Marta in a confirmation e-mail notifying the successful registration.

\subsubsection{Scenario 2}
Yuri cannot afford a car and therefore decides to take advantage of the \emph{PowerEnJoy} service. He accesses the login page from his mobile phone and taps the "sign up" button since he is not a registered user. Then he fills the form providing his license identification number and accepts the Terms and Conditions.

Unfortunately he forgets to fill in his own tax code and the system does not allow him to carry out a successful registration notifying the forgetfulness. Afterwards Yuri completes the procedure by filling the whole form. The system communicates the successful registration and sends him a confirmation e-mail containing PIN and password.

\subsubsection{Use-case}

\subsubsection{Functional requirements}