\subsubsection{Purpose}
This sub-part of the "Use Car" functionality focuses on the sub-functionalities concerned with the interaction between the user and the on-board application in order to allow the user to turn the engine on.

The system will interact with the user prompting him/her after the car has been unlocked and asking to input his/her PIN. This process will grant access to the car systems, hence allowing the user to start the ride.

Right after the engine has been ignited, the on-board application will also start charging the user, all while showing him/her the current charges on the screen, along with the sat-nav that is also going to signal nearby charging stations and the boundaries of the Safe Area.

\subsubsection{Scenario 1}
Francis just unlocked the car he reserved using the \emph{PowerEnJoy} service. He sits on the driver's side and closes the door. The screen of the on-board computer is turned on and the system prompts Francis to insert his PIN. He inserts the 6-digit code correctly; the message \emph{"You can now turn the engine on. Once you do so, the system will start charging you based on the duration of the ride."} appears on the screen. Francis turns the engine on and the system shows him his current charges; he then proceeds to drive the car, starting his ride.

\subsubsection{Scenario 2}
Graham mounted on a \emph{PowerEnJoy} vehicle he just reserved and unlocked. When he inputs the PIN after being prompted by the system, he mistypes one of the 6 digits. The system then shows an error message saying: \emph{"The inserted code is either wrong or does not correspond to the person who reserved this car. Please, retry or use the correct PIN."}. Graham then inserts his code again; this time it is correct, and the system allows him to drive the car.

\subsubsection{Use-case}
A detail of the use-case is provided in Table \ref{start_ride_uc}

\subsubsection{Functional Requirements}
\begin{enumerate}
\item The system must check that the code inserted by the user is correct, which is to say that it corresponds to the right user;
\item The system must start charging the user only after he/she turned the engine on;
\item The system must always notify the user about his/her current charges;
\end{enumerate}

\begin{table}[H]
\begin{center}
\begin{tabular}{p{0.3\textwidth} | p{0.7\textwidth}}
\hline
Actor & User\\
\hline
Goal & Goal 7\\
\hline
Input Condition & The user unlocked the car\\
\hline
Event Flow & 
\begin{enumerate}
\item The user inputs his/her PIN code on the on-board screen;
\item The system analyzes the code and verifies that the code is correct;
\item The system opens the possibility for the user to ignite the engine and start his/her ride.
\end{enumerate} \\
\hline
Output Condition & The ride started, the system started charging the user\\
\hline
Exception & If the user inputs a wrong PIN, the system will notify it and report an error message; in this case, the car still can not be turned on.\\
\hline
\end{tabular}
\end{center}
\caption{Start ride use-case}
\label{start_ride_uc}
\end{table}