The product is a digital management system to support a car-sharing service that exclusively employs electric cars.

The system consists of a back-end server application that manages rental requests remotely and two front-end applications, a web-based one to provide the final user with a friendly interface to take advantage of the services of \hbox{\emph{PowerEnJoy}} and the one that runs on embedded on-board computers of each vehicle, used to interact with the car itself, unlock it and access a personalized GPS/sat-nav service. Moreover, the system will include a mobile application that allows the user to easily access the service anywhere he/she needs to.

The system is intended for only one type of user: drivers, who should be allowed to register and access the system via username and password, in order to make the renting and payment processes easier and quicker to carry out. Moreover, the system aids the users by locating nearby available vehicles and keeps track of the distance driven, all while notifying them about the amount of money they are being charged. Predefined safe parking areas are signaled by an on-board computer.

Lastly, the system aims to motivate drivers to maintain a virtuous behavior providing discounts when it detects signs of responsible and ecologic actions.

In further detail, the goals of \hbox{\emph{PowerEnJoy}} are the following:

\begin{enumerate}
\item Let the user register to the service and login via the provided credentials;
\item Let the driver find the location of nearby available cars;
\item Let him/her reserve a chosen car up to an hour before picking it up;
\item Improve the efficiency of the service by assuring that no car stays reserved if not actually in use;
\item Allow the user to easily access the cars by unlocking them once the driver is in proximity;
\item Actively keep track of the driver's current charges, continuously notifying it;
\item Let the user know which and where the pre-defined parking spots are, showing the nearest ones;
\item Incentivize responsible behaviors, providing discounts for the worthiest users.
\end{enumerate}